\textit{
  This is not a standard competitive programming problem.
  The purpose of this problem is for you to ask for clarification.
}

\textit{
  Notice that the problem setter \textbf{never} intends to make problem statement ambiguous in a real contest,
    but you can ask for clarification if you think there is any ambiguity,
    and you will get two types of response:
  \begin{itemize}
    \item The answer of your question.
    \item \t{`No comment'}, which means the judge thinks your question is clearly covered by problem statement, and you should reread it.
  \end{itemize}
}

\textit{Alright, let's start the problem!}

Cows become unsatisfied with their salary. Bessie, the head cow of farm, tries to negotiate with Farmer John.

\textit{\t{"Moo, Moo, ..."}}, Bessie says.

\textit{\t{"Alright, I know you guys are hardworking, and here is the new plan:"}}, Farmer John says.

\textit{\t{"Each cow will receive \textbf{1} Toffee in it's 1st working day,..."}}, Farmer John says.

\textit{\t{"receive \textbf{2} Toffees in their 2nd working day,..."}}, Farmer John says.

\textit{\t{"and receive \textbf{4} Toffees in their 3rd working day, ..."}}, Farmer John says.

Bessie is very clever, she immediately predicts the salary in the next day, and she goes back to the barn in haste to tell other cows the big news - while Farmer John is still talking.

Farmer John finally finishes his announcement, and starts to worry: 
how many Toffees in total he needs to pay to a cow in the period of $n$ days?
